Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-23 WSSSPE3/report/wg_main_best_practices.tex
Update wg_main_best_practices.tex

%\subsubsection{Why it is important}
Reviewing multiple past articles and talks at different meetings like WSSSPEx \todo{add cites to WSSSPE papers, heroux paper, ...} 
and 
analyzing and promoting sustainable scientific software makes it clear that there 
are several common and recurring ideas that underpin success in developing sustainable software. However, outside of a small community, this knowledge is not widely
shared. This is  especially true for the large community of scientists who generate most of the software used by scientists but are not primarily software developers. In this
scenario, a clear and precise exposition of these best practices collected from many sources and open collaboration among all in the community
in a single source (e.g., journal paper, tutorial)  that can be widely disseminated is necessary and likely to be very valuable.

@@

\noindent{\bf Timeline:}
\begin{itemize}
%
\item 15 Nov: Introduction and scope finished
\item 15 Nov: Sections assigned
\item 31 Jan: Analyzing funding possibilities for survey
\item 31 Jan: First versions of section
\item 15 Feb: Distribution to WSSSPE community
\item 31 Mar: Final version of white paper
\item 30 Apr: Submission of peer-reviewed paper?
\end{itemize}

>>>>

%\subsubsection{Why it is important}
Reviewing multiple past articles and talks at different meetings like WSSSPEx \cite{WSSSPE1, WSSSPE2, 5069157, Blatt_WSSSPE, Ahern_WSSSPE} 
and 
analyzing and promoting sustainable scientific software makes it clear that there 
are several common and recurring ideas that underpin success in developing sustainable software. However, outside of a small community, this knowledge is not widely
shared. This is  especially true for the large community of scientists who generate most of the software used by scientists but are not primarily software developers. In this
scenario, a clear and precise exposition of these best practices collected from many sources and open collaboration among all in the community
in a single source (e.g., journal paper, tutorial)  that can be widely disseminated is necessary and likely to be very valuable.

@@

\noindent{\bf Timeline:}
\begin{itemize}
%
\item 28 Dec: Introduction and scope finished
\item 06 Jan: Sections assigned
\item 31 Jan: Analyzing funding possibilities for survey
\item 31 Jan: First versions of section
\item 15 Feb: Distribution to WSSSPE community
\item 31 Mar: Final version of white paper
\item 30 Apr: Submission of peer-reviewed paper?
\end{itemize}
